---
title: "simpleRegress"
author: "Rita Jarbanda"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Residual standard error: 4.939 on 52 degrees of freedom 72 Multiple R-squared:0.791, Adjusted R-squared:0.7869.

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Residual standard error: 5.376 on 52 degrees of freedom, Adjusted R-squared: 0.7476

```{r}
headlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(headlen)
```

Residual standard error: 4.235 on 52 degrees of freedom,75 Adjusted R-squared:0.8434

```{r}
width <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(width)
summary.lm(width)
```

Residual standard error: 7.32 on 52 degrees of freedom, Adjusted R-squared: 0.5321

```{r}
age <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(age)
```

Residual standard error: 7.5 on 52 degrees of freedom, Adjusted R-Squared: 0.50.

```{r}
weight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(weight)
summary.lm(weight)
```
